\textbf{SPECFEM3D}\\ \textbf{User Manual}

### 2012-09-19 doc/USER_MANUAL/manual_SPECFEM3D.tex
adds point source flags in Par_file related to the use of an inclined force

@@

\end{itemize}
%
\begin{figure}
\noindent \begin{centering}
\includegraphics[width=3in]{figures/gauss_vs_triangle_mod.eps}
\par\end{centering}

@@

{\small }%
\begin{figure}[H]
\noindent \begin{centering}
{\small \includegraphics[width=5in]{figures/source_timing.eps} }
\par\end{centering}{\small \par}

@@

\begin{figure}[ht]
\noindent \begin{centering}
\includegraphics[scale=0.6]{figures/IRIS_band_codes.eps}
\par\end{centering}

>>>>

\item [{\texttt{USE\_FORCE\_POINT\_SOURCE}}] Turn this flag on to use a force source
instead of a \texttt{CMTSOLUTION} moment-tensor source. This can be useful e.g. for oil industry 
foothills simulations in which the source is a vertical force, normal force, 
tilted force, or an impact etc. You will need to give the East, North and vertical components of the force vector;
thus refer to Appendix~\ref{cha:Coordinates} for the orientation of the reference frame.
\item [{\texttt{FACTOR\_FORCE\_SOURCE}}] This parameter specifies the magnitude of the force source.
\item [{\texttt{COMPONENT\_DIR\_VECT\_SOURCE\_E}}] This parameter specifies the East component of 
an arbitrary (non-unitary) direction vector of the force source.
\item [{\texttt{COMPONENT\_DIR\_VECT\_SOURCE\_N}}] This parameter specifies the North component of 
an arbitrary (non-unitary) direction vector of the force source.
\item [{\texttt{COMPONENT\_DIR\_VECT\_SOURCE\_ZUP}}] This parameter specifies the vertical component of 
an arbitrary (non-unitary) direction vector of the force source.

@@

\end{itemize}
%
\begin{figure}
\noindent \begin{centering}
%%%\includegraphics[width=3in]{figures/gauss_vs_triangle_mod.eps}
\includegraphics[width=3in]{figures/gauss_vs_triangle_mod.pdf}
\par\end{centering}

@@

{\small }%
\begin{figure}[H]
\noindent \begin{centering}
{\small \includegraphics[width=5in]{figures/source_timing.pdf} }
\par\end{centering}{\small \par}

@@

\begin{figure}[ht]
\noindent \begin{centering}
\includegraphics[scale=0.6]{figures/IRIS_band_codes.pdf}
\par\end{centering}
